### 2023-06-11 paper/Chapters/Chapter4.tex
Updates
Update the paper

We chose to minimize the reprojection error between the board and back-projected
corners, which were initially detected. The projection and back-projection are
the inverse of each other, hence minimizing the error between the projection of
the board and the detected corners and minimizing the error between the
back-projection of the detected corners and the board are
equivalent. We minimized the error
between the board and the back-projected corners because back-projection does
not require the root finding.

@@

\begin{equation}
	R = R(\theta_x) R(\theta_y) R(\theta_z)
\end{equation}

@@

\begin{align}
	% R_x(\phi)   & =
	% \begin{bmatrix}
	% 	1 & 0          & 0           \\
	% 	0 & \cos(\phi) & -\sin(\phi) \\
	% 	0 & \sin(\phi) & \cos(\phi)
	% \end{bmatrix} \\
	% R_y(\theta) & =
	% \begin{bmatrix}
	% 	\cos(\theta)  & 0 & \sin(\theta) \\
	% 	0             & 1 & 0            \\
	% 	-\sin(\theta) & 0 & \cos(\theta)
	% \end{bmatrix}                 \\
	% R_z(\psi)   & =
	% \begin{bmatrix}
	% 	\cos(\psi) & -\sin(\psi) & 0 \\
	% 	\sin(\psi) & \cos(\psi)  & 0 \\
	% 	0          & 0           & 1
	% \end{bmatrix}
	R(\theta_x) & =
	\begin{bmatrix}
		1 & 0              & 0               \\
		0 & \cos(\theta_x) & -\sin(\theta_x) \\
		0 & \sin(\theta_x) & \cos(\theta_x)
	\end{bmatrix} \\
	R(\theta_y) & =
	\begin{bmatrix}
		\cos(\theta_y)  & 0 & \sin(\theta_y) \\
		0               & 1 & 0              \\
		-\sin(\theta_y) & 0 & \cos(\theta_y)
	\end{bmatrix} \\
	R(\theta_z) & =
	\begin{bmatrix}
		\cos(\theta_z) & -\sin(\theta_z) & 0 \\
		\sin(\theta_z) & \cos(\theta_z)  & 0 \\
		0              & 0               & 1
	\end{bmatrix}
\end{align}

@@

We can compute the intrinsic camera matrices as follows:
\begin{equation}
	K = \begin{pmatrix}
		\frac{f r_x}{s_x} & 0                 & \frac{r_x}{2} \\
		0                 & \frac{f r_y}{s_y} & \frac{r_y}{2} \\
		0                 & 0                 & 1
	\end{pmatrix},
\end{equation}.

@@

To derive the solver for the camera extrinsic parameters, start from
\cref{eq:projection}:
\begin{align}
	\alpha \mathbf{u}                                  & = K f(H\mathbf{X})                  \\
	\alpha K^{-1} \mathbf{u}                           & = f(H\mathbf{X})    &  &
	\text{Move \(K\) to the left side}                                                       \\
	\alpha g( K^{-1}\mathbf{u})                        & = g(f(H\mathbf{X})) &  &
	\text{Set \(\mathbf{\widehat{u}} = K^{-1}\mathbf{u}\); apply \(g(\cdot)\) to both sides} \\
	\alpha \begin{pmatrix}
		       \widehat{u}_x \\ \widehat{u}_y \\ \psi(r(\mathbf{\widehat{u}}))
	       \end{pmatrix}^{T} & = H\mathbf{X}                                 \\
\end{align}

@@

To eliminate the dependency on the scale \(\alpha\), multiply both sides
vectorially by \(g(\mathbf{\widehat{u}})\):
\begin{equation}
	\alpha g(\mathbf{\widehat{u}}) \times g(\mathbf{\widehat{u}})
	= g(\mathbf{\widehat{u}}) \times H\mathbf{X}
	= 0 \implies
	\begin{pmatrix}
		\widehat{u}, \widehat{v}, \psi(r(\mathbf{\widehat{u}}))
	\end{pmatrix}^{T} \times \begin{bmatrix}
		\mathbf{r_1} & \mathbf{r_2} & \mathbf{t}
	\end{bmatrix}^{T} \mathbf{X} = 0
	\label{eq:eq_no_multiplier}
\end{equation}.

From \cref{eq:eq_no_multiplier}, we can see that a point contributes to three
homogeneous equations:
\begin{align}
	\widehat{v} (t_1X + t_2 Y + t_3) -
	g(r(\mathbf{\widehat{u}})) (r_{12}X + r_{22}Y + t_2 ) & = 0
	\label{eq:scaramuzza_system_1}                              \\
	g(r(\mathbf{\widehat{u}})) (r_{11}X + r_{12}Y + t_1) -
	\widehat{u} (t_1X + t_2 Y + t_3)                      & = 0
	\label{eq:scaramuzza_system_2}                              \\
	\widehat{u} (r_{12}X + r_{22}Y + t_2 ) -
	\widehat{v} (r_{11}X + r_{12}Y + t_1)                 & = 0
	\label{eq:scaramuzza_system_3}
\end{align}

Only \cref{eq:scaramuzza_system_3} is linear in the unknowns. Each point gives a
single equation. Now, by rewriting the equation in the matrix form
\(M \cdot H = 0\), where
\[
	H = \begin{pmatrix}
		r_{11}, r_{12}, r_{12}, r_{22}, t_1, t_2
	\end{pmatrix}
\]
we get:
\begin{equation}
	M = \begin{bmatrix}
		-\widehat{v}_1 X_1 & -\widehat{v}_1 Y_1 & -\widehat{u}_1 X_1 & -\widehat{u}_1 Y_1 & -\widehat{v}_1 & -\widehat{u}_1 \\
		\vdots             & \vdots             & \vdots             & \vdots             & \vdots         & \vdots         \\
		-\widehat{v}_N X_N & -\widehat{v}_N Y_N & -\widehat{u}_N X_N & -\widehat{u}_N Y_N & -\widehat{v}_N & -\widehat{u}_N
	\end{bmatrix}
\end{equation}, where \(N\) is the number of points.

The linear estimate of \(H\) is found by minimizing \(\left\lVert M \cdot H
\right\rVert ^{2}\) using SVD. The solution is known up to a scale factor.

To find \(t_1\) and \(t_2 \), note that \(\mathbf{r_1}\) and
\(\mathbf{r_2}\) are orthonormal:
\begin{subnumcases}{}
	\lambda^{2} r_{11} r_{12} + \lambda^{2} r_{12} r_{22} + \lambda^{2} t_1
	t_2  = 0
	\label{eq:orthonormality_1}                                                     \\
	\lambda \sqrt{r_{11}^{2} + r_{12}^{2} + t_1^{2}}                            = 1
	\label{eq:orthonormality_2}                                                     \\
	\lambda \sqrt{r_{12}^{2} + r_{22}^{2} + t_2 ^{2}}                            = 1
	\label{eq:orthonormality_3}
\end{subnumcases},
where \(\lambda\) is non-zero multiplier.

Now, to solve for \(t_1\) and \(t_2 \), first find possible values for
\(t_2 ^{2}\):
\begin{align}
	- \frac{r_{11} r_{12} + r_{12} r_{22}}{t_2 }                  & = t_1 &  &
	\text{Solve eq. (\ref{eq:orthonormality_1}) for \(t_1\)}
	\label{eq:orthonormality_4}                                                \\
	\\
  \sqrt{\lambda^{2} \left( \frac{(r_{11} r_{12} + r_{12} r_{22})^{2}}{t_2 ^{2}} +
	r_{11}^{2} + r_{12}^{2}\right)}                               & = 1   &  &
	\text{Substitute into eq. (\ref{eq:orthonormality_2})}                     \\
  \lambda^{2} \left( \frac{(r_{11} r_{12} + r_{12} r_{22})^{2}}{t_2 ^{2}}\right) +
	r_{11}^{2} + r_{12}^{2}                                      & = 1   &  &
	\text{Square both sides}                                                   \\
  \lambda^{2} \left(\frac{(r_{11} r_{12} + r_{12} r_{22})^{2}}{t_2 ^{2}} \right) +
	r_{11}^{2} + r_{12}^{2} - r_{12}^{2} - r_{22}^{2} - t_2 ^{2} & = 0   &  &
	\text{Subtract eq. (\ref{eq:orthonormality_3})}
	\label{eq:orthonormality_5}
	\\
	\frac{(r_{11} r_{12} + r_{12} r_{22})^{2}}{t_2 ^{2}} +
	r_{11}^{2} + r_{12}^{2} - r_{12}^{2} - r_{22}^{2} - t_2 ^{2}  & = 0   &  &
	\text{Divide both by \(\lambda ^{2}\)}                                     \\
	t_2 ^{4} - (r_{11}^{2} + r_{12}^{2} - r_{12}^{2} -
	r_{22}^{2}) t_2 ^{2} - (r_{11} r_{12} + r_{12} r_{22})^{2}    & = 0   &  &
	\text{Multiply by \(t_2 ^{2}\)}
	\label{eq:orthonormality_6}
\end{align}

Now, solve \cref{eq:orthonormality_6} for \(t_2 ^{2}\), and take a root to find
possible values for \(t_2 \).

To find \(t_1\), substitute the found values for \(t_2 \) into
\cref{eq:orthonormality_4} or \cref{eq:orthonormality_5} depending on the value
of \(t_2 \):
\begin{subnumcases}{}
	t_1  = - \frac{r_{11} r_{12} + r_{12} r_{22}}{t_2 } &
	\text{\(t_2  \neq 0\)} \\
	t_1  =  r_{11}^{2} + r_{12}^{2} - r_{12}^{2} - r_{22}^{2} &
	\text{\(t_2  = 0\)}
\end{subnumcases}

Now, it's possible to find \(H\) for each of the pairs of \(t_1\) and
\(t_2 \).

Lastly, to select the correct \(H\), the author assumes that one of the boards'
corners has the coordinates \( \begin{pmatrix}
	0, 0
\end{pmatrix}^{T}\). Then, the rotation wouldn't affect this
point, and it would be projected to   \(\begin{pmatrix}
	t_1, t_2
\end{pmatrix}^{T}\). Hence, the best matrix would be such that has the closest
\(\begin{pmatrix}
	t_1, t_2
\end{pmatrix}^{T}\) to \(\begin{pmatrix}
	X, Y
\end{pmatrix}^{T}\) of the corner, which is associated with the board's corner
with coordinates \(\begin{pmatrix}
	0, 0
\end{pmatrix}^{T}\).

However, often the algorithm finds who matrices \(H\) such that they have the
same \(t_1\) and \(t_2 \), but different \(r_{11}\), \(r_{12}\), \(r_{21}\). To
find the best matrix, we found the intrinsic values for each of them and
back-projected the board's corners using both matrices.
Then, we used the one which gave the smallest reprojection error.

@@

\begin{equation}
	\begin{bmatrix}
		A_1 \rho_1^{2} & A_1 \rho_1^{4} & -v_1   \\
		C_1 \rho_1^{2} & C_1 \rho_1^{4} & -v_1   \\
		\cdots         & \cdots         & \cdots \\
		A_N \rho_N^{2} & A_N \rho_N^{4} & -v_N   \\
		C_N \rho_N^{2} & C_N \rho_N^{4} & -v_N
	\end{bmatrix} \cdot \begin{bmatrix}
		\lambda_1 \\
		\lambda_2 \\
		t_3
	\end{bmatrix} = \begin{bmatrix}
		B_1 - A_1 \\
		D_1 - C_1 \\
		\cdots    \\
		B_N - A_N \\
		D_N - C_N
	\end{bmatrix}
\end{equation},
where
\begin{align}
	A_i & = r_{21} X_i + r_{22} Y_i + t_2 \\
	B_i & = v_i (r_{31} X_i + r_{32} Y_i) \\
	C_i & = r_{11} X_i + r_{12} Y_i + t_1 \\
	D_i & = u_i (r_{31} X_i + r_{32} Y_i) \\
\end{align}

@@

\begin{equation}
	\begin{aligned}
		c     & =\max \left(s_1^1, s_2^1, s_1^2, s_2^2\right)                                             \\
		s_1^i & =\min \left(\min \left(f_A^i, f_B^i\right)-\mu, \mu-\min \left(f_C^i, f_D^i\right)\right) \\
		s_2^i & =\min \left(\mu-\min \left(f_A^i, f_B^i\right), \min \left(f_C^i, f_D^i\right)-\mu\right) \\
		\mu   & =0.25\left(f_A^i+f_B^i+f_C^i+f_D^i\right)
	\end{aligned}
\end{equation}

>>>>

We minimized the reprojection error between the board and back-projected
corners, which were initially detected. The projection and back-projection are
the inverse of each other, hence minimizing the error between the projection of
the board and the detected corners and minimizing the error between the
back-projection of the detected corners and the board are
equivalent. We minimized the error
between the board and the back-projected corners because back-projection does
not require the root finding.

@@

\begin{equation}
	R = R(\theta_x) R(\theta_y) R(\theta_z),
\end{equation}

@@

\begin{align}
	% R_x(\phi)   & =
	% \begin{bmatrix}
	% 	1 & 0          & 0           \\
	% 	0 & \cos(\phi) & -\sin(\phi) \\
	% 	0 & \sin(\phi) & \cos(\phi)
	% \end{bmatrix} \\
	% R_y(\theta) & =
	% \begin{bmatrix}
	% 	\cos(\theta)  & 0 & \sin(\theta) \\
	% 	0             & 1 & 0            \\
	% 	-\sin(\theta) & 0 & \cos(\theta)
	% \end{bmatrix}                 \\
	% R_z(\psi)   & =
	% \begin{bmatrix}
	% 	\cos(\psi) & -\sin(\psi) & 0 \\
	% 	\sin(\psi) & \cos(\psi)  & 0 \\
	% 	0          & 0           & 1
	% \end{bmatrix}
	R(\theta_x) & =
	\begin{bmatrix}
		1 & 0              & 0               \\
		0 & \cos(\theta_x) & -\sin(\theta_x) \\
		0 & \sin(\theta_x) & \cos(\theta_x)
	\end{bmatrix} \\
	R(\theta_y) & =
	\begin{bmatrix}
		\cos(\theta_y)  & 0 & \sin(\theta_y) \\
		0               & 1 & 0              \\
		-\sin(\theta_y) & 0 & \cos(\theta_y)
	\end{bmatrix} \\
	R(\theta_z) & =
	\begin{bmatrix}
		\cos(\theta_z) & -\sin(\theta_z) & 0 \\
		\sin(\theta_z) & \cos(\theta_z)  & 0 \\
		0              & 0               & 1
	\end{bmatrix}.
\end{align}

@@

We can compute the intrinsic camera matrices as follows:
\begin{equation}
	K = \begin{bmatrix}
		\frac{f r_x}{s_x} & 0                 & \frac{r_x}{2} \\
		0                 & \frac{f r_y}{s_y} & \frac{r_y}{2} \\
		0                 & 0                 & 1
	\end{bmatrix}.
\end{equation}

@@

To derive the solver for the camera extrinsic parameters, start from
\cref{eq:projection}:
\begin{align}
	\alpha \mathbf{u}                                                          & = K f(H\mathbf{X})       \\
	\alpha K^{-1} \mathbf{u}                                                   & = f(H\mathbf{X})    &  &
	\text{Move \(K\) to the left side}                                                                    \\
	\alpha g( K^{-1}\mathbf{u})                                                & = g(f(H\mathbf{X})) &  &
	\text{Set \(\mathbf{\widehat{u}} = K^{-1}\mathbf{u}\); apply \(g(\cdot)\) to both sides}              \\
	\alpha \begin{pmatrix}
		       \widehat{u}_x \\ \widehat{u}_y \\ \psi(r(\mathbf{\widehat{u}}))
	       \end{pmatrix}^{T} & = H\mathbf{X}.
\end{align}

@@

To eliminate the dependency on the scale \(\alpha\), multiply both sides
vectorially by \(g(\mathbf{\widehat{u}})\):
\begin{equation}
	\alpha g(\mathbf{\widehat{u}}) \times g(\mathbf{\widehat{u}})
	= g(\mathbf{\widehat{u}}) \times H\mathbf{X}
	= 0 \implies
	\begin{pmatrix}
		\widehat{u}, \widehat{v}, \psi(r(\mathbf{\widehat{u}}))
	\end{pmatrix}^{T} \times \begin{bmatrix}
		\mathbf{r_1} & \mathbf{r_2} & \mathbf{t}
	\end{bmatrix}^{T} \mathbf{X} = 0
	\label{eq:eq_no_multiplier}.
\end{equation}

From \cref{eq:eq_no_multiplier}, we can see that a point contributes to three
homogeneous equations:
\begin{align}
	\widehat{v} (r_{31}X + r_{32} Y + t_3) -
	g(r(\mathbf{\widehat{u}})) (r_{21}X + r_{22}Y + t_2 ) & = 0
	\label{eq:scaramuzza_system_1}                              \\
	g(r(\mathbf{\widehat{u}})) (r_{11}X + r_{12}Y + t_1) -
	\widehat{u} (r_{31}X + r_{32} Y + t_3)                      & = 0
	\label{eq:scaramuzza_system_2}                              \\
	\widehat{u} (r_{21}X + r_{22}Y + t_2 ) -
	\widehat{v} (r_{11}X + r_{12}Y + t_1)                 & = 0
	\label{eq:scaramuzza_system_3}.
\end{align}

Only \cref{eq:scaramuzza_system_3} is linear in the unknowns. Each point gives a
single equation. Now, by rewriting the equation in the matrix form
\(M \cdot \mathbf{h} = 0\), where
\[
	\mathbf{h} = \begin{pmatrix}
		r_{11}, r_{12}, r_{21}, r_{22}, t_1, t_2
	\end{pmatrix}^{T},
\]
we get:
\begin{equation}
	M = \begin{bmatrix}
		-\widehat{v}_1 X_1 & -\widehat{v}_1 Y_1 & -\widehat{u}_1 X_1 & -\widehat{u}_1 Y_1 & -\widehat{v}_1 & -\widehat{u}_1 \\
		\vdots             & \vdots             & \vdots             & \vdots             & \vdots         & \vdots         \\
		-\widehat{v}_N X_N & -\widehat{v}_N Y_N & -\widehat{u}_N X_N & -\widehat{u}_N Y_N & -\widehat{v}_N & -\widehat{u}_N
	\end{bmatrix}
\end{equation}, where \(N\) is the number of points.

The linear estimate of \(\mathbf{h}\) is found by minimizing \(\left\lVert M \cdot
\mathbf{h} \right\rVert ^{2}\) using SVD. The solution is known up to a scale factor.

To find \(t_1\) and \(t_2 \), note that \(\mathbf{r_1}\) and
\(\mathbf{r_2}\) are orthonormal:
\begin{subnumcases}{}
	\lambda^{2} r_{11} r_{12} + \lambda^{2} r_{21} r_{22} + \lambda^{2} r_{31}
	r_{32}  = 0
	\label{eq:orthonormality_1}                                                     \\
	\lambda \sqrt{r_{11}^{2} + r_{21}^{2} + r_{31}^{2}}                            = 1
	\label{eq:orthonormality_2}                                                     \\
	\lambda \sqrt{r_{12}^{2} + r_{22}^{2} + r_{32} ^{2}}                            = 1
	\label{eq:orthonormality_3},
\end{subnumcases}
where \(\lambda\) is non-zero multiplier.

Now, to solve for \(r_{31}\) and \(r_{32} \), first find possible values for
\(r_{32} ^{2}\):
\begin{align}
	- \frac{r_{11} r_{12} + r_{21} r_{22}}{r_{32} }                         & = r_{31} &  &
	\text{Solve eq. (\ref{eq:orthonormality_1}) for \(r_{31}\)}
	\label{eq:orthonormality_4}
	\\
	\sqrt{\lambda^{2} \left( \frac{(r_{11} r_{12} + r_{21} r_{22})^{2}}{r_{32} ^{2}} +
	r_{11}^{2} + r_{21}^{2}\right)}                                      & = 1   &  &
	\text{Substitute into eq. (\ref{eq:orthonormality_2})}                            \\
	\lambda^{2} \left( \frac{(r_{11} r_{12} + r_{21} r_{22})^{2}}{r_{32} ^{2}} +
	r_{11}^{2} + r_{21}^{2}\right)                                       & = 1   &  &
	\text{Square both sides}                                                          \\
	\lambda^{2} \left(\frac{(r_{11} r_{12} + r_{21} r_{22})^{2}}{r_{32} ^{2}} +
	r_{11}^{2} + r_{21}^{2} - r_{12}^{2} - r_{22}^{2} - r_{32} ^{2} \right) & = 0   &  &
	\text{Subtract eq. (\ref{eq:orthonormality_3})}
	\label{eq:orthonormality_5}
	\\
	\frac{(r_{11} r_{12} + r_{21} r_{22})^{2}}{r_{32} ^{2}} +
	r_{11}^{2} + r_{21}^{2} - r_{12}^{2} - r_{22}^{2} - r_{32} ^{2}         & = 0   &  &
	\text{Divide both by \(\lambda ^{2}\)}                                            \\
	r_{32} ^{4} - (r_{11}^{2} + r_{21}^{2} - r_{12}^{2} -
	r_{22}^{2}) r_{32} ^{2} - (r_{11} r_{12} + r_{21} r_{22})^{2}           & = 0   &  &
	\text{Multiply by \(r_{32} ^{2}\)}
	\label{eq:orthonormality_6}.
\end{align}

Now, solve \cref{eq:orthonormality_6} for \(r_{32} ^{2}\), and take a root to find
possible values for \(r_{32} \).

To find \(r_{31}\), substitute the found values for \(r_{32} \) into
\cref{eq:orthonormality_4} or subtract \cref{eq:orthonormality_3} from
\cref{eq:orthonormality_2} and solve for \(r_{31}\) depending on the value
of \(r_{32} \):
\begin{subnumcases}{}
	r_{31}  = - \frac{r_{11} r_{12} + r_{21} r_{22}}{r_{32} } &
	\text{\(r_{32}  \neq 0\)} \\
	r_{31}  =  r_{11}^{2} + r_{21}^{2} - r_{12}^{2} - r_{22}^{2} &
	\text{\(r_{32}  = 0\)}.
\end{subnumcases}

Now, it's possible to find \(H\) for each of the pairs of \(r_{31}\) and
\(r_{32} \).

Lastly, to select the correct \(H\), the author assumes that one of the boards'
corners has the coordinates \( \begin{pmatrix}
	0, 0
\end{pmatrix}^{T}\). Then, the rotation wouldn't affect this
point, and it would be projected to   \(\begin{pmatrix}
	r_{31}, r_{32}
\end{pmatrix}^{T}\). Hence, the best matrix would be such that has the closest
\(\begin{pmatrix}
	r_{31}, r_{32}
\end{pmatrix}^{T}\) to \(\begin{pmatrix}
	X, Y
\end{pmatrix}^{T}\) of the corner, which is associated with the board's corner
with coordinates \(\begin{pmatrix}
	0, 0
\end{pmatrix}^{T}\).

However, often the algorithm finds who matrices \(H\) such that they have the
same \(r_{31}\) and \(r_{32} \), but different \(r_{11}\), \(r_{21}\), \(r_{12}\). To
find the best matrix, we found the intrinsic values for each of them and
back-projected the board's corners using both matrices.
Then, we used the one which gave the smallest reprojection error.

@@

\begin{equation}
	\begin{bmatrix}
		A_1 \rho_1^{2} & A_1 \rho_1^{4} & -v_1   \\
		C_1 \rho_1^{2} & C_1 \rho_1^{4} & -v_1   \\
		\cdots         & \cdots         & \cdots \\
		A_N \rho_N^{2} & A_N \rho_N^{4} & -v_N   \\
		C_N \rho_N^{2} & C_N \rho_N^{4} & -v_N
	\end{bmatrix} \cdot \begin{bmatrix}
		\lambda_1 \\
		\lambda_2 \\
		t_3
	\end{bmatrix} = \begin{bmatrix}
		B_1 - A_1 \\
		D_1 - C_1 \\
		\cdots    \\
		B_N - A_N \\
		D_N - C_N
	\end{bmatrix},
\end{equation}
where
\begin{align}
	A_i & = r_{21} X_i + r_{22} Y_i + t_2  \\
	B_i & = v_i (r_{31} X_i + r_{32} Y_i)  \\
	C_i & = r_{11} X_i + r_{12} Y_i + t_1  \\
	D_i & = u_i (r_{31} X_i + r_{32} Y_i).
\end{align}

@@

\begin{equation}
	\begin{aligned}
		c     & =\max \left(s_1^1, s_2^1, s_1^2, s_2^2\right)                                             \\
		s_1^i & =\min \left(\min \left(f_A^i, f_B^i\right)-\mu, \mu-\min \left(f_C^i, f_D^i\right)\right) \\
		s_2^i & =\min \left(\mu-\min \left(f_A^i, f_B^i\right), \min \left(f_C^i, f_D^i\right)-\mu\right) \\
		\mu   & =0.25\left(f_A^i+f_B^i+f_C^i+f_D^i\right)
	\end{aligned}.
\end{equation}

### 2023-06-11 paper/Chapters/Chapter5.tex
Update the paper

Also, by using more features, we can get better calibration, as we have more
constraints, but the reprojection error might be higher.

@@

Because of that, we instead artificially removed some of the points from the
detections, to ensure that we can recover them. We also created
artificially occluded points by overlaying a separate image, as it poses
problems for the feature detector.

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}[h]{0.6\linewidth}
		\includegraphics[width=\linewidth]{refined_corners_bad.png}
		\caption{Occlusion on the board with distinct features}
	\end{subfigure}
	\begin{subfigure}[h]{0.6\linewidth}
		\includegraphics[width=\linewidth]{refined_corners_bad_bad.png}
		\caption{Similar pattern to the board in the background}
	\end{subfigure}
	\label{fig:recovered_bad_points}
\end{figure}

>>>>

% Also, by using more features, we can get better calibration, as we have more
% constraints, but the reprojection error might be higher.

@@

The paper's main contribution is finding additional calibration boards' features, which
then can be used as an input to any other camera calibration algorithm. The
measurements' error is assumed to be Gaussian with zero mean and a constant
variance \citep{hartleyMultipleViewGeometry2004}. As calibration process
minimizes the geometric distance between the projected and the measured points,
it is equivalent to performing the maximum likelihood estimation
\citep{hartleyMultipleViewGeometry2004}. As the number of the measurement grows,
the estimated camera parameters converge to the true values, hence adding
additional measurements improves the calibration (especially from the edge of
the image, where the distortion is the highest).

However, the above statement assumes that the measurements are true positives.
To evaluate that, we instead artificially removed some of the points from the
detections, to ensure that we can recover them. We also created
artificially occluded points by overlaying a separate image, as it poses
problems for the feature detector.

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}[h]{0.6\linewidth}
		\includegraphics[width=\linewidth]{refined_corners_bad.png}
		\caption{Occlusion on the board with distinct features}
	\end{subfigure}
	\begin{subfigure}[h]{0.6\linewidth}
		\includegraphics[width=\linewidth]{refined_corners_bad_bad.png}
		\caption{Similar pattern to the board in the background}
	\end{subfigure}
  \caption{Examples of false positives}
	\label{fig:recovered_bad_points}
\end{figure}
